Event History Analyses for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-10-21 manuscript/manuscript.Rmd
update ms.

@panisWhatShapingRT2016 distinguished between automatic response competition effects (bottom-up lateral inhibition between response channels), active and global inhibition effects (top-down nonselective response inhibition), and active and selective inhibition (top-down selective response inhibition). While response competition can be expected to be present in the incongruent trials throughout the experiment, active and global inhibition effects might be present in both congruent and incongruent prime trials. In other words, people learn that the prime-triggered response is premature and that they have to temporarily slow down (increase the global response threshold) in order to allow gating of the target stimulus. This global inhibitory effect might becomes visible in the congruent (compared to no-prime) trials towards the end of the experiment, while it might be masked by the automatic inhibitory effect of response competition in the incongruent trials.

>>>>

@panisWhatShapingRT2016 distinguished between automatic response competition effects (bottom-up lateral inhibition between response channels), active and global inhibition effects (top-down nonselective response inhibition), and active and selective inhibition (top-down selective response inhibition). While automatic response competition can be expected to be present in the incongruent trials throughout the experiment, active and global inhibition effects might be present in both congruent and incongruent prime trials. In other words, people learn that the prime-triggered response is premature and that they have to temporarily slow down (increase the global response threshold) in order to allow gating of the target stimulus. This global inhibitory effect might become visible in the congruent (compared to no-prime) trials towards the end of the experiment, while it might be masked by the automatic inhibitory effect of response competition in the incongruent trials.
Interestingly, while @panisWhatShapingRT2016 did not test interactions between congruency and trial number, they concluded that active (i.e., top-down) response inhibition starts around 360 ms after the onset of the second stimulus (here the target stimulus), which coincides with the onset of the negative effect of congruent primes observed here in trial 1500.
